Transfer learning for echelle spectroscopy

### 2021-12-01 paper/paper1/ms.tex
Add Figure 1 and text around it

Next we identify the spectral lines.  We apply a local-minimum-finding algorithm on the spectrum by defining a prominence threshold $P_{rom} \in (0.005, 0.1)$.  This threshold dictates the number of lines that will be modeled: a lower prominence finds more, weaker lines, and a larger prominence finds fewer, deeper lines.  The prominence algorithm successfully finds lines that reside on top of broad line wings, or unresolved bandheads provided that the individual lines exceed the prominence threshold in their local region.  The number of lines $N_{\mathrm{lines}}$ depends on the bandwidth, prominence, and the intrinsic properties of the input spectrum, principally effective temperature and metallicity.

@@

\begin{figure}[hbt!]
  \centering
  \includegraphics[width=0.5\textwidth]{example-image-a}
  \caption{Number of prominent spectral lines versus effective temperature for PHOENIX models truncated to HPF (\emph{left}) and IGRINS (\emph{right}) bandwidths, for different prominence thresholds of $0.05$ and $0.01$.}
  \label{fig_Nlines_vs_teff}
\end{figure}

Figure \ref{fig_Nlines_vs_teff} shows how the number of detected lines $N_{\mathrm{lines}}$ scales with effective temperature and prominence threshold $P_{rom}$ for the \texttt{PHOENIX} grid, truncated to the bandwidths-plus-buffers for HPF and IGRINS.  The HPF-truncated spectra have $N_s=$335,849 and the IGRINS-truncated spectra have $N_s=$330,052.

@@

Figure \ref{fig_cloned_spectrum_demo} shows a portion of a PHOENIX spectrum cloned with \emph{blas'e}.  The $NN$ epochs of training took X minutes on an RTX2070 GPU with PyTorch v1.11.x, CUDA v11.x, and Intel X CPU, with all tensors as FP64.  That benchmark works out to X seconds per epoch, or about Z seconds per minibatch.

>>>>

Next we identify the spectral lines.  We apply a local-minimum-finding algorithm on the spectrum by defining a prominence threshold $P_{rom} \in (0.005, 0.02)$.  This threshold dictates the number of lines that will be modeled: a lower prominence finds more, weaker lines, and a larger prominence finds fewer, deeper lines.  The prominence algorithm successfully finds lines that reside on top of broad line wings, or unresolved bandheads provided that the individual lines exceed the prominence threshold in their local region.  The number of lines $N_{\mathrm{lines}}$ depends on the bandwidth, prominence, and the intrinsic properties of the input spectrum, principally effective temperature and metallicity.

@@

\begin{figure}[hbt!]
  \centering
  \includegraphics[width=0.5\textwidth]{figures/N_lines_vs_Teff_prom.png}
  \caption{Number of prominent spectral lines versus effective temperature for PHOENIX models truncated to IGRINS (\emph{blue, connected} points) and HPF (\emph{orange, free-standing} points) bandwidths, for different prominence thresholds of $0.02$, $0.01$, and $0.005$.}
  \label{fig_Nlines_vs_teff}
\end{figure}

Figure \ref{fig_Nlines_vs_teff} shows how the number of detected lines $N_{\mathrm{lines}}$ scales with effective temperature and prominence threshold $P_{rom}$ for the \texttt{PHOENIX} grid, truncated to the bandwidths-plus-buffers for HPF and IGRINS.  We see between about 2,000 and 20,000 lines depending on the $T_{\mathrm{eff}}$ and $P_{rom}$.  HPF and IGRINS have comparable number of lines, and halving the prominence increases the number of lines by about $20-30\%$ in these ranges.  The number of lines monotonically increases towards cooler effective temperatures.
The HPF-truncated spectra have $N_s=$335,849 native resolution samples, comparable to the IGRINS-truncated spectra, $N_s=$330,052.

@@

Figure \ref{fig_cloned_spectrum_demo} shows a portion of a PHOENIX spectrum cloned with \emph{blas\'e}.  The $NN$ epochs of training took X minutes on an RTX2070 GPU with PyTorch v1.11.x, CUDA v11.x, and Intel X CPU, with all tensors as FP64.  That benchmark works out to X seconds per epoch, or about Z seconds per minibatch.
